### 2021-05-13 geography/ia/paper.tex
geo ia added

@@

@@

@@

All figures are generated through the use of TikZ (Tantau) and the Python library \verb|matplotlib|. This paper is written with the aid of the typesetting software \LaTeX. On a PDF viewer, the sections in the table of contents can be clicked to access that section. Dataset not included due to large size (\textasciitilde 28000 columns).

>>>>

For our investigation, the topic in question is the environmental quality. We shall compare the environmental quality of two areas, one meant as a residential one and one with a heavy tourist presence. To best represent these areas, we have chosen the XVIe and the VIIe, justifiable as the XVIe is home to many housing complexes and fosters facilities aimed at catering to the residents whereas the VIIe sees many tourists as it is home to the famed Eiffel Tower and the Seine river, prime tourist attractions of Paris.

@@

The method we will be using to select the sites from where we will take the Bipolar survey is Stratified which means that we are choosing the sites ourselves. The reason we chose this is to make sure that we got a good variety of sites that would give a good idea of the general environmental quality of that area, but also to avoid the selection of residential areas, which do in fact exist in the VIIe, which would happen if we chose the random sampling method. This stratified sampling approach would best represent the targeted area and yield meaningful data on tourist-heavy sites.

The sampling method we used to select our sites is the stratified method. The reason for this choice is that we get a

@@

To best retrieve data from our sites, we shall maintain a fair test to uphold the standard and quality of our reliability by getting our data at around the same time on the same day of the week, in an attempt to best match up with the tourists’ habits. We have chosen the time frame of 14:00 to 16:00 on a Friday afternoon, a time frame where tourists will not be constrained by lunch or sleep.

@@

This paper is written with the aid of the typesetting software \LaTeX. On a PDF viewer, the sections in the table of contents can be clicked to access that section.
